% options: font family ('sans' and 'roman'), standard article options
\documentclass[10pt,letterpaper,roman]{moderncv}

% moderncv themes (load first)
% options: casual, classic, oldstyle, banking
\moderncvstyle{classic}

 % options: blue, orange, green, red, purple, grey, black
\moderncvcolor{orange}

\usepackage[osf]{mathpazo}
\usepackage{microtype}
\usepackage{etoolbox}
\usepackage{relsize}
\usepackage{siunitx}
\usepackage[super]{nth}
\usepackage[hscale=0.85,top=.4in,bottom=.3in]{geometry}

% Toggles for various versions. See etoolbox documentation.
\newtoggle{engineering}

% The version
\toggletrue{engineering}

%  default font; use '\sfdefault' for sans serif, '\rmdefault' for
%  roman, or any tex font name
% \renewcommand{\familydefault}{\sfdefault}

% Small caps headings
\renewcommand*\sectionfont{%
  \scshape \lsstyle \fontsize{14}{24}\selectfont%
}

% Italics, not slanted
\renewcommand*{\titlefont}{\large\mdseries\itshape}
\renewcommand*{\addressfont}{\small\mdseries\itshape}

% Pretty ampersand
\let\oldamp\&
\renewcommand\&{{\itshape \oldamp}}

% Pretty Languages
\newcommand\Matlab{\textsc{Matlab}}
\newcommand\Fortran{\textsc{Fortran}}
\newcommand\Unix{\textsc{Unix}}
\newcommand\CC{C%
  \nolinebreak[4]\hspace{-.05em}\raisebox{.25ex}{\relsize{-1}{++}}%
}


% uncomment to suppress page numbering for CVs longer than one page
\nopagenumbers{}

% width of date column
\setlength{\hintscolumnwidth}{1.9cm}

% lists use dashes instead of open bullets
\let\labelitemi\labelitemii

% Short description
\newcommand\cvdesc[2]{%
  \cventry{}%
  {#1}%
  {}%
  {\small #2}%
  {}%
  {}%
}

% Copied from moderncvclassic.cls for the sole purpose of using \itshape
% instead of \slshape in the location slot.
\renewcommand*{\cventry}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
    \ifthenelse{\equal{#4}{}}{}{, {\itshape#4}}%
    \ifthenelse{\equal{#5}{}}{}{, #5}%
    \ifthenelse{\equal{#6}{}}{}{, #6}%
    .\strut%
    \ifx&#7&%
    \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}%
}

% Github and Linkedin footer items
\input{icons.tex}
\newcommand\smallsymbol[1]{\raisebox{-1pt}{#1\hspace{0pt}}}
\newcommand\githubsymbol{\smallsymbol{\githubpic}}
\newcommand\github[1]{\githubsymbol\httplink{#1}}

\newcommand\linkedinsymbol{\smallsymbol{\linkedinpic}}
\newcommand\linkedin[1]{\linkedinsymbol\httplink{#1}}

% personal data
\firstname{Samuel}
\familyname{Britt}

% All the following are optional
\address{3155 Flowers Rd. S Apt. Q}{Atlanta, GA 30341}
\email{sam@britts.us}
\phone{(205)~515~0618}
% \extrainfo{%
%   \github{github.com/samuelbritt}
%   \\ \footersymbol
%   \linkedin{linkedin.com/in/samuelbritt}
% }
% \mobile{(205)~515~0618}
% \fax{+3~(456)~789~012}
% \homepage{www.johndoe.com}
% % \photo[pic-height][frame-thickness]{pic-file}
% \photo[64pt][0.4pt]{picture}

% Optional
% \quote{Some quote (optional)}
\iftoggle{engineering}{
  % \title{Materials Engineer -- Systems Developer}
  \title{From materials engineering to software development through a
  passion for technology.}
  % \title{%\normalsize
  %   Seeking to leverage an engineering background and passion for
  %   technology.
    % to pursue systems software development\\through a passion for
    % technology.
  % }
}{}

\begin{document}
\makecvtitle
\vspace*{-3em}

\section{Education}
\cventry{2011--\phantom{2013}}
  {M.S.}
  {Georgia Institute of Technology}
  {Atlanta, GA}
  {}
  {%
    Computer Science, Specialization in Systems Software.
    \hfill Current GPA: 3.7 \\
    Expected completion: May 2013.
  }

\cventry{2009--2011}
  {Post-Graduate Research}
  {Georgia Institute of Technology}
  {Atlanta, GA}
  {}
  {%
    Completed 2 years of a 4-year Ph.D.\ program in Materials
    Engineering.
    \hfill GPA: 3.9 \\
    Modeling and simulation research in mechanics of $\alpha$+$\beta$
    titanium alloys.
  }

\cventry{2004--2009}
  {B.S.\ with Highest Honors}
  {Georgia Institute of Technology}
  {Atlanta, GA}
  {}
  {Materials Science and Engineering. \hfill GPA: 4.0}

\section{Skills \& Technologies}
\cvitem{Proficient:}{C, Python (and SciPy), Git, Mercurial, \Unix,
  Linux, Vim, \LaTeX.}
\cvitem{Familiar:}{\CC, Java, \Matlab, \Fortran, SQL, GDB, OpenMPI,
  Eclipse, Android development.}

\section{Experience}

\cventry{2012--2013}
  {Teaching Assistant, Database Systems}
  {Georgia Institute of Technology}
  {Atlanta, GA}
  {}
  {
    \begin{itemize}
      \item Advised students in class of over $240$. Graded student
        projects.
      \item Held one-on-one meetings to teach high-level concepts such
        as entity-relationship data modeling, as well as technical
        help in implementing database-driven applications using MySQL
        and PHP.
    \end{itemize}
  }

\cventry{2012}
  {User-Level Threading Library, Class Project}
  {Georgia Institute of Technology}
  {Atlanta, GA}
  {}
  {
    \begin{itemize}
      \item Developed a C threading library that allowed user-defined
        thread scheduling. The professor selected the library to be
        used in future course offerings.
    \end{itemize}
  }

\cventry{2009--2011}
  {Post-Graduate Research}
  {Georgia Institute of Technology}
  {Atlanta, GA}
  {}
  {
    Studied the mechanical response and texture evolution of
    $\alpha$+$\beta$ titanium alloys via multiscale modeling and
    simulation.
    \begin{itemize}
      \item Developed new, thermally activated constitutive model
        based on unique properties of the titanium microstructure.
      \item Implemented crystal plasticity material model in \Fortran\
        to enhance finite element simulation software.
      \item Built microstructure generation code and post-processing
        routines using \CC, \Matlab, and Python.
      \item Presented results regularly at the meetings of the Center
        for Computational Materials Design.
      \item Administered the Red Hat Linux computer clusters used by
        all students in the research group.
    \end{itemize}
  }

\cventry{2005--2009}
  {Engineering Intern}
  {Southern Research Institute}
  {Birmingham, AL}
  {}
  {%
    Five terms as an engineering co-op, performing high-temperature
    materials research for the aerospace industry.
    \begin{itemize}%
      \item Investigated the kinetics of phenolic resin pyrolysis
        using isothermal and nonisothermal thermogravimetry at
        temperatures up to \SI{1100}{\celsius}. Co-authored a report
        that was presented at the \nth{56} JANNAF Propulsion Meeting.
      \item Designed a facility capable of thermogravimety and
        dilatometry of carbon-phenolics up to \SI{650}{\celsius} under
        pressures up to \SI{4.15}{\mega\pascal}.
      \item Coordinated effort to develop, build, and test a facility
        capable of tensile permeability tests up to
        \SI{1900}{\celsius}.
      % \item Oversaw operation and maintenance of a permeability
      %   facility testing carbon-phenolic composites up to
      %   \SI{1300}{\celsius}.
    \end{itemize}
  }

\newlength\coursesep
\setlength{\coursesep}{1.3ex}
\section{Advanced Coursework}
\cvitem[\coursesep]{Computer Science}{Adv.\ Operating Systems,
  Real-Time \& Embedded Systems, Computability and Algorithms, HPC
  Architecture, Applied Cryptography, Internet Computing, Software
  Engineering: Analysis \& Testing.}
\cvitem[\coursesep]{Modeling \& Simulation}{Statistics \& Numerical
  Methods, Parallel Scientific Computing, Adv.\ Constitutive Relations
  of Solids, Continuum Mechanics, Quantitative Characterization of
  Materials.}
\cvitem{Materials Engineering}{Mechanical Behavior of Composites,
  Thermodynamics of Materials, Kinetics of Phase Transformations,
  Studies in structure-property relationships of alloys, ceramics,
  polymers, semiconductors, and composites.}


\section{Scholarships \& Awards}
\cvdesc{Henry Ford Award}{for the most outstanding academic record in
  the junior engineering class}
% \cvdesc{Wohlford Co-Op Scholarship}{for outstanding contributions to
%   Tech and high scholastic achievement}
% \cvdesc{Chapman-Pentecost Scholarship}{for most outstanding
%   academic record as a junior MSE student}
% \cvdesc{Blount Scholarship}{for outstanding academic performance
%   as an engineering student from Alabama}
\cvdesc{President's Scholarship}{Tech's premier merit-based
  scholarship awarded to approximately \SI{2}{\percent} of students}
\cvdesc{National Merit Scholarship}{awarded to the top
  \SI{0.6}{\percent} of the \num{1.4} million or so high school
  applicants}
% \cvdesc{S.\ Truett Cathy Scholar Award}{awarded to the top $25$
%   Chick-fil-A employees nationwide for demonstrated excellence in the
%   areas of work, education, community and personal leadership
%   development}
% \cvdesc{Chick-fil-A Leadership Scholarship}{for demonstrated
%   excellence in the areas of work, education, community and
%   personal leadership development}

\end{document}

% Samples...

\section{Experience}
\subsection{Vocational}
\cvitem{description}{item}
\cvitemwithcomment{Language 1}{Skill level}{Comment}
\cvlistitem{Item 1}
\cvlistitem{Item 2}
\cvlistitem{Item 3}
\cvdoubleitem{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
\cventry{year--year}{Job title}{Employer}{City}{}{General description
  no longer than 1--2 lines.\newline{}%
  Detailed achievements:%
  \begin{itemize}%
    \item Achievement 1;
    \item Achievement 3.
\end{itemize}}

% change the symbol for lists
\renewcommand{\listitemsymbol}{-~}

\section{Extra 2}
\cvlistdoubleitem{Item 1}{Item 4}
\cvlistdoubleitem{Item 2}{Item 5}%\cite{book1}}
\cvlistdoubleitem{Item 3}{}

\end{document}
